---
layout: post
title: "Basic post with R and maths"
date: "2016-03-04 00:22:40 +1000"
categories: [jekyll, rstats]
tags: [knitr, servr]
use_math: true
---

Jekyll is wonderful, and Github pages a gift from the open-source gods, but for a lot of us __Markdown__ isn't quite enough. I wanted to be able to use R code, to make really reproducible reports, etc. If you got hooked on doing this quickly and easily using __Rstudio__, you'll know what I mean.
This template lets you write posts in __.Rmarkdown__ format, (.Rmd), just like in Rstudio.


I'll talk later (or somewhere else) about adding maths (i.e. greek letters and formulas).

Hint: add this to *_config.yml*: `mathjax: true`, and add this to files in *_layouts* (not sure which ones, works for me...)

````{html eval=FALSE}
<script type="text/javascript"
  src="http://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML">
</script>
````


## Some R code to test

```{r }
summary(cars)
```



```{r}
options(digits = 3)
cat("hello world!")
set.seed(123)
(x = rnorm(40) + 10)
# generate a table
knitr::kable(head(mtcars))
(function() {
  if (TRUE) 1 + 1  # a boring comment
})()
names(formals(servr::jekyll))  # arguments of the jekyll() function
```

Just to test inline R expressions[^2] in **knitr**, we know the first element in `x` (created in the code chunk above) is `r x[1]`. You can certainly draw some graphs as well:

[^2]: The syntax in R Markdown for inline expressions is `` `r code` ``, where `code` is the R expression that you want to evaluate, e.g. `x[1]`.

```{r cars, fig.height=5, fig.width=7, fig.cap='A scatterplot of the cars data'}
par(mar = c(4, 4, .1, .1))
plot(cars, pch = 19, col = 'red')  # a scatterplot
```
